Easy as Pi: A Network Coding Raspberry Pi Testbed

### 2016-05-31 schemes.tex
Finished RLNC ...for now

In \eqref{eq:recoded_packet}, $w_{ij}$ is the coding coefficient used
in the $i$-th recoded packet and assigned to multiply a previously coded
packet $C_j$. These coding coefficients are again uniformly and randomly chosen
from $GF(q)$. Still, each of the $w_{ij}$ are not the appended recoding
coefficients for signalling since the they will only retrieve previously
coded packets. The analytical expression for the appended recoding
coefficients is obtained by calculating recoded packets as function of the
original packets. Therefore, we define the local coding matrix $\textbf{W}$
in the same way as it was made for $\textbf{V}$. Thus, the local coding matrix
can be written as:
%
\begin{align} \label{eq:local_coding_matrix}
\textbf{W} =
\left[
\begin{array}{c}
        w_1    \\ \hline
        \vdots \\ \hline
        w_g    \\
\end{array}
\right]
=
\left[
\begin{array}{ccc}
        w_{11} & \ldots & w_{1g} \\
        \vdots  & \ddots & \vdots  \\
        w_{g1} & \ldots & w_{gg} \\
\end{array}
\right]
\end{align}
%
With the definitions from \eqref{eq:coding_matrix} and
\eqref{eq:local_coding_matrix}, the recoded packets
$\textbf{R} = \left[R_1 \ldots R_g \right]^T$ are written as
$\textbf{R} = (\textbf{W} \textbf{V}) \textbf{P}$. Here, we recognize
the relationship between original and recoded packets. The resulting
coding matrix is simply the multiplication of matrices $\textbf{W}$ and
$\textbf{V}$. Denoting ${(\textbf{W} \textbf{V})}_{ij}$ as the element
in the $i$-th row and $j$-th column of $(\textbf{W} \textbf{V})$, this
term is the resulting coding coefficient used to create $R_i$ after
encoding the original packet $P_j$ recoding it locally in an intermediate
node. In this case, we have assumed that recoding has taken place at the
closesBy doing some algebra, these terms can be verified to be computed
as:
%
\begin{align}
\label{eq:appended_coded_coefficients}
{(\textbf{W} \textbf{V})}_{ij} = \sum_{k=1}^{g} w_{ik} v_{kj}\ ,\ \forall i,j \in [1,g] \times [1,g]
\end{align}
%
Similarly as with encoding, any decoder that collects a set
of $g$ \ac{l.i.} recoded packets with their respective $w_i$, will be able to
decode the data as mentioned before in Section \ref{sssec:decoding}. Finally,
the appended coding coefficients for decoding

>>>>

In \eqref{eq:recoded_packet}, $w_{ij}$ is the coding coefficient used
in the $i$-th recoded packet and assigned to multiply a previously coded
packet $C_j$. These coding coefficients are again uniformly and randomly chosen
from $GF(q)$. Still, each of the $w_{ij}$ are not the appended recoding
coefficients for signalling since the they will only retrieve previously
coded packets. The analytical expression for the appended coefficients
after recoding is obtained by calculating recoded packets as function of the
original packets. Therefore, we define the local coding matrix $\textbf{W}$
in the same way as it was made for $\textbf{V}$. Thus, the local coding matrix
can be written as:
%
\begin{align} \label{eq:local_coding_matrix}
\textbf{W} =
\left[
\begin{array}{c}
        w_1    \\ \hline
        \vdots \\ \hline
        w_g    \\
\end{array}
\right]
=
\left[
\begin{array}{ccc}
        w_{11} & \ldots & w_{1g} \\
        \vdots  & \ddots & \vdots  \\
        w_{g1} & \ldots & w_{gg} \\
\end{array}
\right]
\end{align}
%
With the definitions from \eqref{eq:coding_matrix} and
\eqref{eq:local_coding_matrix}, the recoded packets
$\textbf{R} = \left[R_1 \ldots R_g \right]^T$ are written as
$\textbf{R} = (\textbf{W} \textbf{V}) \textbf{P}$. Here, we recognize
the relationship between original and recoded packets. The resulting
coding matrix is simply the multiplication of matrices $\textbf{W}$ and
$\textbf{V}$. Denoting ${(\textbf{W} \textbf{V})}_{ij}$ as the element
in the $i$-th row and $j$-th column of $(\textbf{W} \textbf{V})$, this
term is the resulting coding coefficient used to create $R_i$ after
encoding the original packet $P_j$ recoding it locally in an intermediate
node. Finally, the appended coefficients for $R_i$ are
${(\textbf{W} \textbf{V})}_{ik}$ with $k \in [1,g]$. By doing some
algebra, each ${(\textbf{W} \textbf{V})}_{ij}$ term can be verified to be
computed as:
%
\begin{align}
\label{eq:appended_coded_coefficients}
{(\textbf{W} \textbf{V})}_{ij} = \sum_{k=1}^{g} w_{ik} v_{kj}\ ,\ \forall i,j \in [1,g] \times [1,g]
\end{align}
%
This procedure is carried by all the recoders in a given network, therefore
keeping the structure of the recoded packets for any decoder to compute
the Gaussian elimination. Similarly as with encoding, any decoder that
collects a set of $g$ \ac{l.i.} recoded packets with their respective
${(\textbf{W} \textbf{V})}_{ij}$, will be able to decode the data as mentioned before in Section \ref{sssec:decoding}.
